Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory

### 2020-10-27 papers/thesis-kirstie/thesis.tex
new Xi in the plot

 \begin{figure}[h!]
    \centering
    \includegraphics[height=6cm]{weight_functions.pdf}
    \caption{\color{red}RERUN for NEW XI!\color{black}Shows how the weight functions $w_0$, $w_1$, $w_2$, $w_3$ vary along the 
    z-axis for a reduced temperature of 2}
    \label{fig:weight_functions}
  \end{figure}

 \begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.4\linewidth}
      \includegraphics[height=5cm]{W2.png}
      \caption{A crossectional view of $w_2$}
    \end{subfigure} 
    \begin{subfigure}[b]{0.4\linewidth}
      \includegraphics[height=5cm]{W3.png}
      \caption{A crossectional view of $w_3$}
    \end{subfigure} 
    \caption{\color{red}RERUN for NEW XI!\color{black}Cross-sectional views of the 3D weight functions. (a) $w_2$ is a 
    spherical shell in 3D with soft edges. Weight functions $w_0$ and $w_1$ 
    have a similar shape. (b) $w_3$ is a sphere with soft edges in 3D.}
    \label{fig:W0andW3}
    \end{figure} 
\color{black}

>>>>

 \begin{figure}[h!]
    \centering
    \includegraphics[height=6cm]{weight_functions.pdf}
    \caption{The weight functions $w_0$, $w_1$, $w_2$, $w_3$ vary along the 
    z-axis for a reduced temperature of 2.}
    \label{fig:weight_functions}
  \end{figure}

 \begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.4\linewidth}
      \includegraphics[height=5cm]{W2.png}
      % \includegraphics[width=5cm]{figs/w2-ring}
      \caption{A crossectional view of $w_2$}
    \end{subfigure} 
    \begin{subfigure}[b]{0.4\linewidth}
      \includegraphics[height=5cm]{W3.png}
      \caption{A crossectional view of $w_3$}
    \end{subfigure} 
    \caption{Cross-sectional views of the 3D weight functions. (a) $w_2$ is a 
    spherical shell in 3D with soft edges. Weight functions $w_0$ and $w_1$ 
    have a similar shape. (b) $w_3$ is a sphere with soft edges in 3D.}
    \label{fig:W0andW3}
    \end{figure} 
\color{black}
